Network graphs in ggraph

### 2016-02-15 104-network-graphs-in-ggraph.Rmd
State to state network graph

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(igraph)
library(ggplot2)
library(ggraph)
load("cache/corpus-lsh.rda")
```

@@

```{r}
ggraph(codes_g, "igraph", algorithm = "kk") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 6) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name)) +
  labs(title = "Code to code borrowings") +
  theme(legend.position = "bottom")
```

>>>>

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(igraph)
library(ggplot2)
library(ggraph)
library(stringr)
load("cache/corpus-lsh.rda")
source("R/helper.R")
set.seed(82892)
```

@@

```{r}
ggraph(codes_g, "igraph", algorithm = "kk") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 6) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name)) +
  labs(title = "Code to code borrowings") +
  theme(legend.position = "bottom")
```

Now make a plot of state to state borrowings.

```{r}
min_state_sections <- 100
max_state_connections <- 2

states_edges <- summary_matches %>% 
  mutate(borrower_state = extract_state(borrower_code),
         match_state = extract_state(match_code),
         borrower_date = extract_date(borrower_code),
         match_date = extract_date(match_code)) %>% 
  filter(!is.na(match_code),
         borrower_date >= match_date,
         borrower_state != match_state) %>% 
  group_by(borrower_state, match_state) %>% 
  summarize(sections_borrowed = sum(sections_borrowed)) %>% 
  filter(sections_borrowed >= 100) %>% 
  top_n(max_state_connections, sections_borrowed)

state_nodes <- read.csv("regions.csv")

states_g <- graph_from_data_frame(states_edges, directed = TRUE,
                                  vertices = state_nodes) 
```

Now plot it.

```{r}
ggraph(states_g, "igraph", algorithm = "graphopt") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(size = 6, alpha = 0.75, aes(color = region)) +
  geom_node_text(aes(label = name)) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
  ggforce::theme_no_axes() +
  labs(title = "State to state borrowings") +
  theme(legend.position = "bottom")
```
